Reproducibility in Plant Pathology

### 2018-06-01 README.rmd
Fix authors in citation
Update Zach's initials in author listing
Minor reformatting

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
16.04 LTS.

@@

(+61) (7) 4831 1948   e. adam.sparks@usq.edu.au
https://staffprofile.usq.edu.au/Profile/Adam-Sparks

>>>>

Sparks et al. XXXX

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
17.10.

@@

(+61) (7) 4831 1948   adam.sparks@usq.edu.au
https://staffprofile.usq.edu.au/Profile/Adam-Sparks
